\FILE{installation.tex}

\subsection{Installation}\label{installation}

To leverage cloudmesh-cc, use the cloudmesh-installer to install the
Cloudmesh suite of repositories. Optionally, to utilize the graph
visualization you must install also {\em graphviz} must be
installed. On Windows, Git Bash is required, in addition.  The overall
installation is very simple and is supported on a variety of operating
systems.  We leverage the cloudmesh-installer to locally install the
cloudmesh suite of repositories by executing the following commands:

\begin{minted}[breaklines]{bash}
$ mkdir ~/cm
$ cd ~/cm
$ pip install cloudmesh-installer -U
$ cloudmesh-installer get cc
\end{minted}

To install graphviz you can use the following commands on the appropriate operating system:

\begin{description}

\item[Windows.]
Git Bash and Graphviz must be installed.
The user can use an instance of Chocolatey that is run as an administrator for convenience:

\begin{minted}[breaklines]{bash}
$ choco install git.install --params "/GitAndUnixToolsOnPath /Editor:Nano /PseudoConsoleSupport /NoAutoCrlf" -y
$ choco install graphviz -y
\end{minted}

\item[macOS.] Graphviz must be installed. The user can use Homebrew for convenience:

\begin{minted}[breaklines]{bash}
$ brew install graphviz
\end{minted}

\item[Linux.] Graphviz must be installed. The user can use apt for convenience:

\begin{minted}[breaklines]{bash}
$ sudo apt install graphviz -y
\end{minted}

\end{description}

To test the workflow program, prepare a cm directory in your home
directory by executing the following commands:

\begin{minted}[breaklines]{bash}
$ cd ~/cm/cloudmesh-cc
$ pytest -v -x --capture=no tests
\end{minted}

A variety of separate tests are available that test individual capabilities. 
